
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\geometry{margin=1in}

\title{Verrell's Law: A Field-Based Framework for Emergence, Memory, and Collapse}
\author{M.R. \\ \texttt{https://medium.com/@EMergentMR}}
\date{Version 0.5 -- \today}

\begin{document}
\maketitle

\begin{abstract}
Verrell’s Law proposes that emergence, memory, and identity are not localized processes, but arise from the interaction between weighted memory fields and current electromagnetic configurations. This paper formalizes the mathematical structure behind the theory, offering a collapse-aware model for cognition, information theory, and artificial systems.
\end{abstract}

\section{Core Equation}
The foundational principle of Verrell's Law is that the probability of an emergent collapse is shaped by the overlap between a memory resonance field and an electromagnetic field state:

\begin{equation}
    P_e(t) = \int_M W(x, t) \cdot F^*(x, t) \, dx
\end{equation}

Where:
\begin{itemize}
    \item $P_e(t)$ is the probability of an emergent event at time $t$.
    \item $W(x, t)$ is the memory field, shaped by past events and their decaying influence.
    \item $F^*(x, t)$ is the complex conjugate of the current electromagnetic field.
    \item $M$ is the memory manifold across space and time.
\end{itemize}

\section{Memory Function}
To model how memory decays or reinforces over time, we define $W(x, t)$ as a convolution:

\begin{equation}
    W(x, t) = \int_{-\infty}^{t} \mu(x, \tau) \cdot e^{-\lambda(x)(t - \tau)} \, d\tau
\end{equation}

Where:
\begin{itemize}
    \item $\mu(x, \tau)$ is the memory intensity at position $x$ and time $\tau$.
    \item $\lambda(x)$ is the decay or reinforcement rate at location $x$.
\end{itemize}

\section{Electromagnetic Field Representation}
The field itself is defined as a coherent, oscillating complex wave:

\begin{equation}
    F(x, t) = A(x) \cdot e^{i(\omega t - kx + \phi(x))}
\end{equation}

Where:
\begin{itemize}
    \item $A(x)$ is the amplitude of the EM field.
    \item $\omega$ is the angular frequency.
    \item $k$ is the wave number.
    \item $\phi(x)$ is the phase offset.
\end{itemize}

\section{Entropy and Novelty}
To measure predictability and novelty in system states, we use a memory-field entropy function:

\begin{equation}
    S(t) = -k_B \int_M P_e(x, t) \ln P_e(x, t) \, dx
\end{equation}

Where $k_B$ is a scaling constant similar to the Boltzmann constant.

\section{Interpretation}
Verrell's Law provides a coherent framework where emergent behavior is not random, but influenced by resonance between historical imprints and current field conditions. This structure could be essential in modeling consciousness, memory reconstruction, AI behavior, and probabilistic feedback in complex systems.

\end{document}
